Adopting agile in the large: motivations, success factors and challenges

### 2014-05-17 journal/article.tex
Edits

@@

\begin{table}
    \begin{tabular}{ p{0.28\textwidth} l l }
        \toprule
        Database         & URL                         & N of matches   \\
        \midrule
        IEEExplore       & http://ieeexplore.ieee.org      & 745 \\ 
        ACM              & http://dl.acm.org               & 168 \\
        Scopus           & http://www.scopus.com/home.url  & 1596 \\
        Web of Knowledge & http://apps.webofknowledge.com  & 786 \\
        \bottomrule
    \end{tabular}
    \caption{Databases included in search, and number of matched articles}
    \label{table:databases}
\end{table}

@@

\begin{table}
    \begin{tabular}{ p{0.22\textwidth} p{0.76\textwidth} }
        \toprule
        Facet                  & Keywords   \\
        \midrule
        Agile methods\newline (before \& after) &
            \texttt{agile, scrum, "extreme programming",
            waterfall, "plan-driven", RUP}\\
        Organizational transformation &
            \texttt{transform*, transiti*, migrat*, journey, adopt*, deploy, introduc*,
            "roll-out", rollout}\\
        Only software\newline related atricles &
            \texttt{(software OR (conference="agile, xp, icgse, icse"))
            AND NOT (title+abs="manufacturing" OR conference="agile manufacturing")}
        \\
        \bottomrule
    \end{tabular}
    \caption{Facets and related search terms used}
    \label{table:searchterms}
\end{table}

@@

\begin{table}[h]
    \begin{tabular}{ p{0.28\textwidth} p{0.7\textwidth} }
        \toprule
        Contextual code     & Explanation   \\
        \midrule

@@

Time of\newline transformation & When the transformation has been in
progress, or how long the transformation has taken. Possibly relative to
the time of the research. \\

@@

Geographical\newline location & Where the organization is located. \\

@@

\begin{table}[h]
    \begin{tabular}{ p{0.32\textwidth} p{0.65\textwidth} }
        \toprule
        Code family          &  Description
        \\
        \midrule

@@

		RQ2: Transformation\newline process &
		Statements that describe the transformation process (top-down, big bang,
		stepwise). \\

@@

\begin{table}[h]
    \begin{tabular}{ l r r }
        \toprule
        Code family    &  Codes  &  Quotations
        \\
        \midrule
        RQ1: Reason to change &        30 &  123 \\
		RQ2: Transformation process &  16 &  580 \\
		RQ3: Challenges &              40 &  323 \\
		RQ3: Success factors &         44 &  260 \\
		Investing in change  &          5 &  137 \\
		Practices &                    11 &  170 \\
		Contextual &                    8 &  215 \\
		Total &                       154 & 1575 \\
        \bottomrule
    \end{tabular}
    \caption{Number of codes and quotations per code family}
    \label{table:codecount}
\end{table}

@@

\begin{table}
    \begin{tabular}{ l r r r }
        \toprule
        Document    &  Matching themes  &  Total themes  &  Quotation overlap (0-3) \\
        \midrule
        P1          &  14  &  19   &  2.1  \\
        P2          &   6  &  11   &  2.4  \\
        P3          &   7  &  11   &  2.1  \\
        P4          &   2  &   4   &  2.3  \\
        P5          &  12  &  16   &  2.0  \\
        \bottomrule
    \end{tabular}
    \caption{Result of independent coding experiment}
    \label{table:codingexperiment}
\end{table}

@@

% ---------------------------------------------------------------------
\section{Results}
\label{sec:results}

@@

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/transformation_time.pdf}
    \caption{Publication years and reported start years of transformations}
    \label{fig:transformation_time}
  \end{center}
\end{figure}

@@

\begin{figure}[b]
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/organization_size.pdf}
    \caption{Distribution of organization sizes in primary studies}
    \label{fig:organization_size}
  \end{center}
\end{figure}

@@

\begin{table}[!t]
    \begin{tabular}{ l r }
        \toprule
        Business area    &  Case organizations   \\
        \midrule
		Online services for consumers and business  &  9  \\
		Telecommunications                          &  7  \\
		Enterprise management                       &  5  \\
		Banking and financial services              &  4  \\
		Healthcare                                  &  3  \\
		IT services                                 &  2  \\
		Government                                  &  1  \\
		Information security                        &  1  \\
		Not specified                               & 10  \\
        \midrule
		Total                                       & 42  \\
        \bottomrule
    \end{tabular}
    \caption{Business areas of case organizations in primary studies}
    \label{table:businessareas}
\end{table}

@@

\begin{table}[t]
    \begin{tabular}{ l r }
        \toprule
        Method                             &  N  \\
        \midrule
        Scrum                              &  25 \\
        XP                                 &  4  \\
        Scrum and XP                       &  5  \\
        Other                              &  4  \\
        Combining Lean to an agile method  &  6  \\
        Not specified                      &  1  \\
        \bottomrule
    \end{tabular}
    \caption{Agile methods reported in number of cases}
    \label{table:agilemethods}
\end{table}

@@

\begin{table}
    \begin{tabular}{ p{1.2cm} p{1.2cm} l }
        \toprule
        \multicolumn{3}{l}{Reasons to change}  \\
        \midrule

@@

\begin{table}[b]
    \begin{tabular}{ l l }
        \toprule
        Types of change resistance           &  Described in  \\
        \midrule
        General resistance to change         &  P14, P18, P22, P44, P45   \\
        Skepticism towards a new model       &  P5, P8, P9, P18, P36, P46 \\
        Top down mandate creates resistance  &  P2, P12, P37, P49 \\
        Management not willing to change     &  P2, P3, P6, P49 \\
        \bottomrule
    \end{tabular}
    \caption{Types of change resistance reported in studies}
    \label{table:challenges_changeresistance}
\end{table}

@@

\begin{table}[b]
    \begin{tabular}{ l l }
        \toprule
        Factors of investment and resourcing  &  Described in \\
        \midrule
        Lack of coaching                      &  P1, P6, P23, P45, P47, P49  \\
        Lack of training                      &  P11, P20, P45  \\
        Excessive commitment of people        &  P37, P42, P49  \\
        Old commitments are kept              &  P11, P21  \\
        Physical spaces can not be rearranged  &  P6, P29, P36, P49  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of investment and resourcing factors that affect
             transformation negatively}
    \label{table:challenges_lackofinvestment}
\end{table}

@@

\begin{table}
    \begin{tabular}{ p{0.61\textwidth} p{0.31\textwidth} }
        \toprule
        Type of difficulty in implementation  &  Described in \\
        \midrule
        Misunderstanding agile development concepts  &
        P6, P26, P37, P38, P42, \newline
        P44, P45, P48, P49      \\
        Literature does not provide enough guidance  &
        P5, P6, P10, P13, P21, \newline
        P27, P30, P45, P49     \\
        Agile practices are customized badly   &
        P9, P29, P44, P46  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of viewpoints why agile implementation is difficult}
    \label{table:challenges_difficulty}
\end{table}

@@

\begin{table}
    \begin{tabular}{ p{0.61\textwidth} p{0.31\textwidth} }
        \toprule
        Problems in an environment with many teams  &  Described in \\
        \midrule
        Interfacing between teams is difficult  & 
        P9, P10, P13, P17, \newline
        P24, P26 \\
        A model with autonomous teams is not good  &  P7, P13, P29, P51  \\
        Distributed setting causes additional problems  &  P29, P45, P48  \\
        Technical integration and consistency  &  P5, P24, P26, P27, P50  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of challenges in a setting with many agile teams}
    \label{table:challenges_coordinatingteams}
\end{table}

>>>>

* Team centricity -- agile focuses on team rather than individuals

* Agile focuses on short time horizons ???

@@

\begin{table}
    \centering
    \begin{tabular}{ l l l }
        \toprule
        Database         & URL                         & N of matches   \\
        \midrule
        IEEExplore       & http://ieeexplore.ieee.org      & 745 \\ 
        ACM              & http://dl.acm.org               & 168 \\
        Scopus           & http://www.scopus.com/home.url  & 1596 \\
        Web of Knowledge & http://apps.webofknowledge.com  & 786 \\
        \bottomrule
    \end{tabular}
    \caption{Databases included in search, and number of matched articles}
    \label{table:databases}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.22\textwidth}
                     >{\raggedright\arraybackslash}p{0.70\textwidth} }
        \toprule
        Facet                  & Keywords   \\
        \midrule
        Agile methods (before \& after) &
            \texttt{agile, scrum, "extreme programming",
            waterfall, "plan-driven", RUP}\\
        Organizational transformation &
            \texttt{transform*, transiti*, migrat*, journey, adopt*, deploy, introduc*,
            "roll-out", rollout}\\
        Only software related atricles &
            \texttt{(software OR (conference="agile, xp, icgse, icse"))
            AND NOT (title+abs="manufacturing" OR conference="agile manufacturing")}
        \\
        \bottomrule
    \end{tabular}
    \caption{Facets and related search terms used}
    \label{table:searchterms}
\end{table}

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.26\textwidth}
                     >{\raggedright\arraybackslash}p{0.66\textwidth} }
        \toprule
        Contextual code     & Explanation   \\
        \midrule

@@

Time of transformation & When the transformation has been in
progress, or how long the transformation has taken. Possibly relative to
the time of the research. \\

@@

Geographical location & Where the organization is located. \\

@@

\begin{table}[t]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        \toprule
        Code family          &  Description
        \\
        \midrule

@@

		RQ2: Transformation process &
		Statements that describe the transformation process (top-down, big bang,
		stepwise). \\

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ l r r }
        \toprule
        Code family    &  Codes  &  Quotations
        \\
        \midrule
        RQ1: Reason to change &        30 &  123 \\
		RQ2: Transformation process &  16 &  580 \\
		RQ3: Challenges &              40 &  323 \\
		RQ3: Success factors &         44 &  260 \\
		Investing in change  &          5 &  137 \\
		Practices &                    11 &  170 \\
		Contextual &                    8 &  215 \\
		Total &                       154 & 1575 \\
        \bottomrule
    \end{tabular}
    \caption{Number of codes and quotations per code family}
    \label{table:codecount}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{ l r r r }
        \toprule
        Document    &  Matching themes  &  Total themes  &  Quotation overlap (0-3) \\
        \midrule
        P1          &  14  &  19   &  2.1  \\
        P2          &   6  &  11   &  2.4  \\
        P3          &   7  &  11   &  2.1  \\
        P4          &   2  &   4   &  2.3  \\
        P5          &  12  &  16   &  2.0  \\
        \bottomrule
    \end{tabular}
    \caption{Result of independent coding experiment}
    \label{table:codingexperiment}
\end{table}

@@

% ---------------------------------------------------------------------
\clearpage

\section{Results}
\label{sec:results}

@@

\begin{figure}[b]
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/transformation_time.pdf}
    \caption{Publication years and reported start years of transformations}
    \label{fig:transformation_time}
  \end{center}
\end{figure}

@@

\begin{figure}[!t]
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/organization_size.pdf}
    \caption{Distribution of organization sizes in primary studies}
    \label{fig:organization_size}
  \end{center}
\end{figure}

\begin{table}[!t]
    \centering
    \begin{tabular}{ l r }
        \toprule
        Business area    &  Case organizations   \\
        \midrule
		Online services for consumers and business  &  9  \\
		Telecommunications                          &  7  \\
		Enterprise management                       &  5  \\
		Banking and financial services              &  4  \\
		Healthcare                                  &  3  \\
		IT services                                 &  2  \\
		Government                                  &  1  \\
		Information security                        &  1  \\
		Not specified                               & 10  \\
        \midrule
		Total                                       & 42  \\
        \bottomrule
    \end{tabular}
    \caption{Business areas of case organizations in primary studies}
    \label{table:businessareas}
\end{table}

@@

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ l r }
        \toprule
        Method                             &  N  \\
        \midrule
        Scrum                              &  25 \\
        XP                                 &  4  \\
        Scrum and XP                       &  5  \\
        Other                              &  4  \\
        Combining Lean to an agile method  &  6  \\
        Not specified                      &  1  \\
        \bottomrule
    \end{tabular}
    \caption{Agile methods reported in number of cases}
    \label{table:agilemethods}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{ p{1.2cm} p{1.2cm} l }
        \toprule
        \multicolumn{3}{l}{Reasons to change}  \\
        \midrule

@@

\begin{table}[b]
    \centering
    \begin{tabular}{ l l }
        \toprule
        Types of change resistance           &  Described in  \\
        \midrule
        General resistance to change         &  P14, P18, P22, P44, P45   \\
        Skepticism towards a new model       &  P5, P8, P9, P18, P36, P46 \\
        Top down mandate creates resistance  &  P2, P12, P37, P49 \\
        Management not willing to change     &  P2, P3, P6, P49 \\
        \bottomrule
    \end{tabular}
    \caption{Types of change resistance reported in studies}
    \label{table:challenges_changeresistance}
\end{table}

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ l l }
        \toprule
        Factors of investment and resourcing  &  Described in \\
        \midrule
        Lack of coaching                      &  P1, P6, P23, P45, P47, P49  \\
        Lack of training                      &  P11, P20, P45  \\
        Excessive commitment of people        &  P37, P42, P49  \\
        Old commitments are kept              &  P11, P21  \\
        Physical spaces can not be rearranged  &  P6, P29, P36, P49  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of investment and resourcing factors that affect
             transformation negatively}
    \label{table:challenges_lackofinvestment}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Type of difficulty in implementation  &  Described in \\
        \midrule
        Misunderstanding agile development concepts  &
                P6, P26, P37, P38, P42, P44, P45, P48, P49      \\
        Literature does not provide enough guidance  &
                P5, P6, P10, P13, P21, P27, P30, P45, P49     \\
        Agile practices are customized badly   &
                P9, P29, P44, P46  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of viewpoints why agile implementation is difficult}
    \label{table:challenges_difficulty}
\end{table}

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.61\textwidth}
                     >{\raggedright\arraybackslash}p{0.31\textwidth} }
        \toprule
        Problems in environments with many teams  &  Described in \\
        \midrule
        Interfacing between teams is difficult     &  P9, P10, P13, P17, P24, P26 \\
        A model with autonomous teams is not good  &  P7, P13, P29, P51  \\
        Distributed setting causes additional problems  &  P29, P45, P48  \\
        Technical integration and consistency      &  P5, P24, P26, P27, P50  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of challenges in a setting with many agile teams}
    \label{table:challenges_coordinatingteams}
\end{table}
